---
title: "`r params$set_title`"
author: "`r params$set_author`"
date: "`r Sys.Date()`"
params:
  printcode: no
  printwarning: no
  storecache: no
  set_title: "Measurement Report"
  set_author: "Michael Wu"
  template: !expr system.file("templates", "input_template.xlsx", package = "mrautomatr")
  item: TRUE
  descriptive: TRUE
  ds_plot: TRUE
  efa_screeplot: TRUE
  cfa_model_fit: TRUE
  cfa_model_plot: TRUE
  cfa_model_parameters: TRUE
  cfa_model_thresholds: FALSE # default is to mute the thresholds (set to TRUE to have it shown in Appendix)
  cfa_r2: TRUE
  internal_reliability: TRUE
  summary_item_statistics: TRUE
  item_total_statistics: TRUE
  inv_tx: TRUE
  inv_gender: TRUE
  inv_age: TRUE
  inv_lg: TRUE
  correlation_matrix_lg: TRUE
  correlation_matrix_bivar: TRUE
  correlation_matrix_item: FALSE # this might crash the document, so the default is FALSE
output: 
  officedown::rdocx_document:
    mapstyles:
      Normal: ['First Paragraph']
    reference_docx: !expr system.file("templates", "MR_word_template.docx", package = "mrautomatr")
---

```{r setup, include = F}
# knitr global settings
knitr::opts_chunk$set(
  echo = TRUE, 
  fig.cap = TRUE,
  echo = params$printcode, 
  warning = params$printwarning, 
  cache = params$storecache,
  message = F,
  error = T,
  results="asis",
  tab.cap.style = "Table Caption",
  tab.cap.pre = "Table ",
  tab.cap.sep = ": ",
  fig.cap.style = "Image Caption",
  fig.cap.pre = "Figure ",
  fig.cap.sep = ": ")

options(yaml.eval.expr = TRUE)
```

```{r, include = F}
# vertical and horizontal page margin set up
ps <- officer::prop_section(
  page_margins = officer::page_mar(
    bottom = 1,
    top = 1,
    right = 1,
    left = 1,
    header = 0.5,
    footer = 0.5,
    gutter = 0),
  type = "continuous"
)
```

```{r user input}
# predefined excel sheets
user_path <- openxlsx::read.xlsx(params$template, sheet = 1)
user_subscale <- openxlsx::read.xlsx(params$template, sheet = 2)
user_model <- openxlsx::read.xlsx(params$template, sheet = 3)
user_description <- openxlsx::read.xlsx(params$template, sheet = 4)

# load paths
year <- user_path$year
measure <- user_path$measure

# need to evaluate box_path() if specified
data_file_path <- 
  if(grepl("^box_path", user_path$data_file_path) == T){
    eval(parse(text = user_path$data_file_path))
  } else {
    user_path$data_file_path
  }
  
fs_data_file_path <- 
  if(grepl("^box_path", user_path$fs_data_file_path) == T){
    eval(parse(text = user_path$fs_data_file_path))
  } else {
    user_path$fs_data_file_path
  }
  
model_file_path <- 
  if(grepl("^box_path", user_path$model_file_path) == T){
    eval(parse(text = user_path$model_file_path))
  } else {
    user_path$model_file_path
  }
  
# specify items for each subscale, without wave subscript (ordered by wave)
subscale_data <- BBmisc::convertColsToList(user_subscale)

  # a vector of all items for the current construct 
subset_data <- as.character(
  unlist(
    lapply(subscale_data, 
           function(x) x[!is.na(x)])
    )
  )

# a vector of EFA models (ordered by wave)
model_efa <- na.omit(user_model$model_efa)

# a vector of CFA models (ordered by wave)
model_cfa <- na.omit(user_model$model_cfa)

# a list of treatment invariance models (config, metric and scalar; ordered by wave)
model_inv_tx <- split.list(na.omit(user_model$model_inv_tx), 3)
  
# a list of gender invariance models (config, metric and scalar; ordered by wave)
model_inv_gender <- split.list(na.omit(user_model$model_inv_gender), 3)

# a list of age invariance models (config, metric and scalar; ordered by wave)
model_inv_age <- split.list(na.omit(user_model$model_inv_age), 3)

# the longitudinal invariance model
model_inv_lg <- split.list(na.omit(user_model$model_inv_lg), 1)
```

```{r data preparation}
# read in data (currently accepting dta, xlsx and csv)
dat <- read.any(data_file_path)

# subset of only items for the current construct
dat_s <- as.data.frame(
  dplyr::select(dat, 
                dplyr::all_of(subset_data)))

# subscale and its corresponding item names
subscale_item_name <- as.data.frame(subscale_data) %>%
  tidyr::gather(key = "subscale", 
                value = "item") %>%
  dplyr::mutate(wave = gsub("(.*)(_)(\\d+)", "\\3", subscale),
                wave = paste("T", wave, sep = ""),
                subscale = gsub("(.*)(_)(\\d+)", "\\1", subscale)) %>%
  dplyr::select(subscale, wave, item) %>% 
  tidyr::drop_na()

# read in factor score data (only for calculating bivariate correlation)
if(is.null(read.any(fs_data_file_path)) == T){
    stop("Factor score data file path is not specified, please double check. Also, please make sure that the factor score dataset has the subscale names as variable names, the same as the ones specified in user_subscale.",call. = F)} else{
    dat_fs <- read.any(fs_data_file_path) %>%
                dplyr::select(names(user_subscale))
    }
```


`r officer::block_section(ps)`
\newpage

## Table of content

<!---BLOCK_TOC--->

## List of figures

<!---BLOCK_TOC{seq_id: 'fig'}--->

## List of tables

<!---BLOCK_TOC{seq_id: 'tab'}--->

`r officer::block_section(ps)`
\newpage

## Measure Description

\newpage

## Data and Sample

```{r item, tab.cap="Item description", tab.id = "item", eval = params$item}
# remove the auto-created dots when reading in excel sheets
names(user_description) <- gsub("\\.", " ", names(user_description))

flextable::flextable(user_description) %>%
  flextable::align(part = "all") %>%
  flextable::font(fontname = "Times", part = "all") %>% 
  flextable::line_spacing(space = 1) %>%
  flextable::set_table_properties(layout = "autofit")
```

`r officer::block_section(ps)`
\newpage

## Method

...

`r officer::block_section(ps)`
\newpage

## Results

`r officer::block_section(ps)`

### Descriptive Statistics

```{r descriptive, tab.cap="Descriptive statistics", tab.id = "descriptive", eval = params$descriptive}
ds <- skimr::skim(dat_s) %>% 
  dplyr::mutate_if(is.numeric, round, 3) %>%
  dplyr::rename_with( ~ gsub("^(numeric.)(.*)$", "\\2", .x),
                      dplyr::starts_with("numeric.")) %>%
  dplyr::select(-skim_type, -hist) %>%
  dplyr::rename(variable = skim_variable)
  
flextable::flextable(ds) %>%
  flextable::align(part = "all") %>%
  flextable::font(fontname = "Times", part = "all") %>% 
  flextable::bold(part = "header") %>%
  flextable::italic(j = 6:10, part = "header") %>%
  flextable::fontsize(size = 10, part = "body") %>% 
  flextable::line_spacing(space = 1) %>%
  flextable::set_table_properties(layout = "autofit")
```

`r officer::block_section(ps)`
\newpage

```{r ds_plot, fig.cap = "Item distribution", fig.id = "ds_plot", fig.height = 8, fig.width = 6, dpi = 300, eval = params$ds_plot}

# descriptive plots

par(mfrow = c(6,6),
    mar = c(4,1,1,1))

chunk_num <- ncol(dat_s) %/% 24

# If number of plot is fewer than 24
if(chunk_num == 0){
  
  for(i in 1:ncol(dat_s)){
    hist(dat_s[, i], main = "", xlab = names(dat_s)[i], col = "white")
  }
  
} else{

# If number of plot is more than 24
  while (chunk_num >= 1) {
    
  for (i in 1:24) {
    index <- 24*(chunk_num - 1) + i

    hist(dat_s[, index], main = "", xlab = names(dat_s)[index], col = "white")
  }

  chunk_num <- chunk_num - 1
  }
  
}
```

`r officer::block_section(ps)`
\newpage

<!---BLOCK_LANDSCAPE_START--->

### Factor Analysis

#### EFA and CFA
```{r efa_screeplot, fig.cap = "EFA model screeplots at all waves", fig.id = "efa_screeplot", fig.height = 4, fig.width = 9, dpi = 300, eval = params$efa_screeplot}

df_efa <- sup.cat(
  purrr::map_dfr(
    lapply(model_efa, 
           get.eigenvalue, 
           path = model_file_path),
    dplyr::bind_rows))

ggplot2::ggplot(df_efa, ggplot2::aes(x = nfactor, y = ev)) +
  ggplot2::geom_point() +
  ggplot2::geom_line() +
  ggplot2::scale_x_continuous(breaks = seq(0, max(df_efa$nfactor), by = 2)) +
  ggplot2::facet_wrap(~ wave) +
  ggplot2::labs(x = "\nComponent Number", y = "Eigenvalue\n") + 
  ggplot2::theme_classic()
```

\newpage

```{r cfa_model_fit, tab.cap = "CFA model fits at all waves", tab.id = "cfa_model_fit", eval = params$cfa_model_fit}

df_cfa <- sup.cat(
  purrr::map_dfr(
    lapply(model_cfa, 
           get.cfa.fit, 
           path = model_file_path),
    dplyr::bind_rows))

flextable::flextable(df_cfa) %>%
    flextable::compose(
    part = "header", j = "ChiSq",
    value = flextable::as_paragraph("\U03C7", flextable::as_sup("2"))
    ) %>%
  flextable::align(part = "all") %>%
  flextable::font(fontname = "Times", part = "all") %>%
  flextable::bold(part = "header") %>%
  flextable::italic(j = 4, part = "header") %>%
  flextable::fontsize(size = 10, part = "body") %>% 
  flextable::set_table_properties(layout = "autofit")
```

\newpage

```{r cfa_model_plot, fig.cap = "CFA model final factor structure", fig.id = "cfa_model_plot", fig.height = 4, fig.width = 8, fig.align='center', dpi = 300, eval = params$cfa_model_plot}

if(length(unique(sapply(sup.cat(lapply(model_cfa, get.est, path = model_file_path)), nrow))) > 1){
  stop("The factor structure has to be the same across waves in order to draw the graph. Please check all CFA models.", call. = F)
}

plot_label <- sup.cat(
  purrr::map_dfc(
    lapply(model_cfa, 
           get.est, 
           path = model_file_path), 
    dplyr::bind_cols)) %>%
  tidyr::unite("label", tidyr::everything(), sep = "")

model_cfa_str <- sup.cat(
  MplusAutomation::readModels(
    file.path(model_file_path, 
              model_cfa[[1]]))
  )

par(mfrow = c(1,1))
semPlot::semPaths(model_cfa_str, style="lisrel", layout = "tree",
         nCharNodes = 5, sizeMan = 4, sizeMan2 = 4, sizeLat = 8, 
         thresholds = F, residuals = F, intercepts = F, edge.color = "gray40", 
         edgeLabels = plot_label$label, edge.label.cex = 0.3,
         edge.label.position = 0.8, label.cex = 1, mar=c(1,1,3,1))
```

\newpage

```{r cfa_model_parameters, tab.cap = "CFA model parameters at all waves", tab.id = "cfa_model_parameters", eval = params$cfa_model_parameters}
df_cfa_modparam <- sup.cat(
  lapply(model_cfa, 
         get.modparam, 
         path = model_file_path) %>% 
  purrr::reduce(dplyr::left_join, 
                by = c("paramHeader", "param")))

flextable::flextable(df_cfa_modparam) %>%
  flextable::align(part = "all") %>%
  flextable::font(fontname = "Times", part = "all") %>%
  flextable::bold(part = "header") %>%
  flextable::fontsize(size = 10, part = "body") %>% 
  flextable::set_table_properties(layout = "autofit")
```

\newpage

```{r cfa_r2, tab.cap = "CFA model R-squared at all waves", tab.id = "cfa_r2", eval = params$cfa_r2}

df_cfa_r2 <- sup.cat(
  lapply(model_cfa, 
         get.R2, 
         path = model_file_path)) %>% 
  purrr::reduce(dplyr::left_join, 
                by = c("param"))

flextable::flextable(df_cfa_r2) %>%
  flextable::align(part = "all") %>%
  flextable::font(fontname = "Times", part = "all") %>%
  flextable::bold(part = "header") %>%
  flextable::fontsize(size = 10, part = "body") %>% 
  flextable::set_table_properties(layout = "autofit")
```

\newpage

#### Internal Reliability and Correlations

```{r internal_reliability, tab.cap = "Internal reliability by each subscale", tab.id = "internal_reliability", eval = params$internal_reliability}

# (example: https://rpubs.com/hauselin/reliabilityanalysis)

alpha_drop = list()

for(i in 1:length(subscale_data)){
  
 alpha_drop[[i]] <- psych::alpha(
   dplyr::select(dat_s, 
          na.omit(
            dplyr::all_of(subscale_data[[i]])
            )
          ),
   check.keys = T,
   )$alpha.drop
  
}

alpha_drop <- purrr::map_dfr(alpha_drop, dplyr::bind_rows) %>% 
            round(digits = 3) %>%
            tibble::rownames_to_column("item") %>%
  dplyr::mutate(item = gsub("\\.\\.\\.(\\d+)$", "", item)) %>% 
  dplyr::left_join(subscale_item_name, by = "item") %>%
  dplyr::select(subscale, wave, tidyr::everything())

alpha_drop <- flextable::as_grouped_data(alpha_drop, 
                                         groups = c( "wave","subscale"))


flextable::as_flextable(alpha_drop) %>%
  flextable::align(part = "all") %>%
  flextable::font(fontname = "Times", part = "all") %>% 
  flextable::bold(part = "header") %>%
  flextable::fontsize(size = 10, part = "body") %>% 
  flextable::set_table_properties(layout = "autofit")
```

\newpage

```{r summary_item_statistics, tab.cap = "Summary item statistics by each subscale", tab.id = "summary_item_statistics", eval = params$summary_item_statistics}

item_stats = list()

for(i in 1:length(subscale_data)){
  
 item_stats[[i]] <- psych::alpha(
   dplyr::select(dat_s, 
          na.omit(
            dplyr::all_of(subscale_data[[i]])
            )
          ),
   check.keys = T,
   )$item.stats
  
}

item_stats <- purrr::map_dfr(item_stats, dplyr::bind_rows) %>% 
            round(digits = 3) %>%
            tibble::rownames_to_column("item") %>%
  dplyr::mutate(item = gsub("\\.\\.\\.(\\d+)$", "", item)) %>% 
  dplyr::left_join(subscale_item_name, by = "item") %>%
  dplyr::select(subscale, tidyr::everything())

item_stats <- flextable::as_grouped_data(item_stats, 
                                         groups = c( "wave","subscale"))

flextable::as_flextable(item_stats) %>%
  flextable::align(part = "all") %>%
  flextable::font(fontname = "Times", part = "all") %>%
  flextable::bold(part = "header") %>%
  flextable::fontsize(size = 10, part = "body") %>% 
  flextable::set_table_properties(layout = "autofit")
```

\newpage

```{r item_total_statistics, tab.cap = "Item total statistics", tab.id = "item_total_statistics", eval = params$item_total_statistics}

total_stats = list()

for(i in 1:length(subscale_data)){
  
 total_stats[[i]] <- psych::alpha(
   dplyr::select(dat_s, 
          na.omit(
            dplyr::all_of(subscale_data[[i]])
            )
          ),
   check.keys = T,
   )$total
  
}

# a list of omega by wave
omega_by_wave_ls <- sup.cat(
  lapply(model_cfa, 
         get.omega.bywave, 
         path = model_file_path))

# add wave tag to subscale
for (i in 1:length(omega_by_wave_ls)) {
  omega_by_wave_ls[[i]]$subscale_wave <- paste(omega_by_wave_ls[[i]]$subscale_wave,
                                          i,
                                          sep = "_")
}


total_stats <- purrr::map_dfr(total_stats, dplyr::bind_rows) %>% 
            round(digits = 3) %>%
            dplyr::mutate(subscale_wave = unique(
              paste(subscale_item_name$subscale,
                    gsub("^(T)(\\d+)$","\\2", subscale_item_name$wave),
                    sep = "_"))
            ) %>%
  {if (is.empty(unlist(model_inv_lg)) == F) 
    dplyr::left_join(.,sup.cat(get.omega.lg(model = model_inv_lg[3],
                                            path = model_file_path)), 
            by = "subscale_wave") else .} %>% 
  dplyr::left_join(purrr::map_dfr(omega_by_wave_ls, 
                                  dplyr::bind_rows),
                   by = "subscale_wave") %>% # merge in omega squared 
  dplyr::mutate(wave = gsub("(.*)(_)(\\d+)", "\\3", subscale_wave),
                wave = paste("T", wave, sep = ""),
                subscale = gsub("(.*)(_)(\\d+)", "\\1", subscale_wave)) %>%
  dplyr::select(subscale, wave, tidyr::everything(), -subscale_wave)

if(sum(is.na(total_stats$omega_lg)) > 0){
  stop("Omega from longitudinal model is not showing up, potentially because: 1) the longitudinal model is not specified; or 2) subscale/item names are different in the excel sheet and in the longitudinal invariance model. Please double check and make sure to always add an underscore and a wave tag (_#) in the subscale section to both the construct name and the item names in your excel sheet and in your Mplus input file before you run the model. For Mplus models, you may need to rename your variables (i.e. add wave tags) before you run the models. If you only have one wave, simply use (_1) as a wave tag, and the number 1 will be picked up as the wave tag in the tables in this report.")
}

if(sum(is.na(total_stats$omega_by_wave)) > 0){
  stop("Omega from CFA model by wave is not showing up, potentially because: 1) the CFA model is not specified; or 2) subscale/item names are different in the excel sheet and in the CFA models. Please double check and make sure to always add an underscore and a wave tag (_#) in the subscale section to both the construct name and the item names in your excel sheet and in your Mplus input file before you run the model. For Mplus models, you may need to rename your variables (i.e. add wave tags) before you run the models. If you only have one wave, simply use (_1) as a wave tag, and the number 1 will be picked up as the wave tag in the tables in this report.")
}

total_stats <- flextable::as_grouped_data(total_stats, 
                                          groups = c( "wave"))

flextable::as_flextable(total_stats) %>%
  flextable::align(part = "all") %>%
  flextable::font(fontname = "Times", part = "all") %>% 
  flextable::bold(part = "header") %>%
  flextable::fontsize(size = 10, part = "body") %>% 
  flextable::set_table_properties(layout = "autofit")
```

\newpage

#### Measurement Invariance

```{r inv_tx, tab.cap = "Treatment group invariance model fit", tab.id = "inv_tx", eval = params$inv_tx}

df_inv_tx <- sup.cat(
  purrr::map_dfr(
    lapply(model_inv_tx, 
           get.invariance.fit, 
           path = model_file_path), 
    dplyr::bind_rows)
  )

df_inv_tx <- df_inv_tx %>%
  dplyr::mutate(wave = gsub("^([a-zA-Z]+)(\\d+)(.*)", "\\2", Filename), 
                .before = "Parameters") %>%
  dplyr::mutate(wave = paste("T", wave, sep = ""))

df_inv_tx <- flextable::as_grouped_data(df_inv_tx, 
                                        groups = c("wave"))


flextable::as_flextable(df_inv_tx) %>% 
  flextable::compose(
    part = "header", j = "ChiSqM_Value",
    value = flextable::as_paragraph("\U03C7",
                                    flextable::as_sup("2"))
    ) %>%
  flextable::compose(
    part = "header", j = "ChiSqBaseline_Value",
    value = flextable::as_paragraph("\U03C7",
                                    flextable::as_sup("2"), 
                                    flextable::as_sub("B"))
    ) %>%
  flextable::compose(
    part = "header", j = "ChiSqDiffTest_Value",
    value = flextable::as_paragraph(paste("\u0394","\U03C7", sep = ""),
                                    flextable::as_sup("2"))
    ) %>%
  flextable::align(part = "all") %>%
  flextable::font(fontname = "Times", part = "all") %>%
  flextable::bold(part = "header") %>%
  flextable::fontsize(size = 10, part = "body") %>% 
  flextable::italic(j = c(4,7,10), part = "header") %>%
  flextable::set_header_labels(
    Parameters = "k",
    ChiSqM_DF = "df",
    ChiSqM_PValue = "p",
    ChiSqBaseline_DF = "df",
    ChiSqBaseline_PValue = "p",
    ChiSqDiffTest_DF = "df",
    ChiSqDiffTest_PValue = "p",
    RMSEA_Estimate = "RMSEA"
  )  %>%
  flextable::set_table_properties(layout = "autofit")

```

\newpage

```{r inv_gender, tab.cap = "Gender invariance model fit", tab.id = "inv_gender", eval = params$inv_gender}

df_inv_gender <- sup.cat(
  purrr::map_dfr(
    lapply(model_inv_gender, 
           get.invariance.fit, 
           path = model_file_path),
    dplyr::bind_rows))

df_inv_gender <- df_inv_gender %>%
  dplyr::mutate(wave = gsub("^([a-zA-Z]+)(\\d+)(.*)", "\\2", Filename), 
                .before = "Parameters") %>%
  dplyr::mutate(wave = paste("T", wave, sep = ""))

df_inv_gender <- flextable::as_grouped_data(df_inv_gender, 
                                            groups = c("wave"))

flextable::as_flextable(df_inv_gender) %>% 
  flextable::compose(
    part = "header", j = "ChiSqM_Value",
    value = flextable::as_paragraph("\U03C7",
                                    flextable::as_sup("2"))
    ) %>%
  flextable::compose(
    part = "header", j = "ChiSqBaseline_Value",
    value = flextable::as_paragraph("\U03C7",
                                    flextable::as_sup("2"), 
                                    flextable::as_sub("B"))
    ) %>%
  flextable::compose(
    part = "header", j = "ChiSqDiffTest_Value",
    value = flextable::as_paragraph(paste("\u0394","\U03C7", sep = ""), 
                                    flextable::as_sup("2"))
    ) %>%
  flextable::align(part = "all") %>%
  flextable::font(fontname = "Times", part = "all") %>%
  flextable::bold(part = "header") %>%
  flextable::fontsize(size = 10, part = "body") %>% 
  flextable::italic(j = c(4,7,10), part = "header") %>%
  flextable::set_header_labels(
    Parameters = "k",
    ChiSqM_DF = "df",
    ChiSqM_PValue = "p",
    ChiSqBaseline_DF = "df",
    ChiSqBaseline_PValue = "p",
    ChiSqDiffTest_DF = "df",
    ChiSqDiffTest_PValue = "p",
    RMSEA_Estimate = "RMSEA"
  )  %>%
  flextable::set_table_properties(layout = "autofit")

```

\newpage

```{r inv_age, tab.cap = "Age invariance model fit", tab.id = "inv_age", eval = params$inv_age}

df_inv_age <- sup.cat(
  purrr::map_dfr(
    lapply(model_inv_age, 
           get.invariance.fit, 
           path = model_file_path), 
    dplyr::bind_rows))

df_inv_age <- df_inv_age %>%
  dplyr::mutate(wave = gsub("^([a-zA-Z]+)(\\d+)(.*)", "\\2", Filename), 
                .before = "Parameters") %>%
  dplyr::mutate(wave = paste("T", wave, sep = ""))

df_inv_age <- flextable::as_grouped_data(df_inv_age, 
                                         groups = c("wave"))

flextable::as_flextable(df_inv_age) %>% 
  flextable::compose(
    part = "header", j = "ChiSqM_Value",
    value = flextable::as_paragraph("\U03C7",
                                    flextable::as_sup("2"))
    ) %>%
  flextable::compose(
    part = "header", j = "ChiSqBaseline_Value",
    value = flextable::as_paragraph("\U03C7",
                                    flextable::as_sup("2"), 
                                    flextable::as_sub("B"))
    ) %>%
  flextable::compose(
    part = "header", j = "ChiSqDiffTest_Value",
    value = flextable::as_paragraph(paste("\u0394","\U03C7", sep = ""), 
                                    flextable::as_sup("2"))
    ) %>%
  flextable::align(part = "all") %>%
  flextable::font(fontname = "Times", part = "all") %>%
  flextable::bold(part = "header") %>%
  flextable::fontsize(size = 10, part = "body") %>% 
  flextable::italic(j = c(4,7,10), part = "header") %>%
  flextable::set_header_labels(
    Parameters = "k",
    ChiSqM_DF = "df",
    ChiSqM_PValue = "p",
    ChiSqBaseline_DF = "df",
    ChiSqBaseline_PValue = "p",
    ChiSqDiffTest_DF = "df",
    ChiSqDiffTest_PValue = "p",
    RMSEA_Estimate = "RMSEA"
  )  %>%
  flextable::set_table_properties(layout = "autofit")
```

\newpage

```{r inv_lg, tab.cap = "Longitudinal invariance model fit", tab.id = "inv_lg", eval = params$inv_lg}

df_inv_lg <- sup.cat(
  get.invariance.fit(
    model_inv_lg, 
    path = model_file_path)
  )

flextable::flextable(df_inv_lg) %>% 
  flextable::compose(
    part = "header", j = "ChiSqM_Value",
    value = flextable::as_paragraph("\U03C7",
                                    flextable::as_sup("2"))
    ) %>%
  flextable::compose(
    part = "header", j = "ChiSqBaseline_Value",
    value = flextable::as_paragraph("\U03C7",
                                    flextable::as_sup("2"), 
                                    flextable::as_sub("B"))
    ) %>%
  flextable::compose(
    part = "header", j = "ChiSqDiffTest_Value",
    value = flextable::as_paragraph(paste("\u0394","\U03C7", sep = ""), 
                                    flextable::as_sup("2"))
    ) %>%
  flextable::align(part = "all") %>%
  flextable::font(fontname = "Times", part = "all") %>%
  flextable::bold(part = "header") %>%
  flextable::fontsize(size = 10, part = "body") %>% 
  flextable::italic(j = c(4,7,10), part = "header") %>%
  flextable::set_header_labels(
    Parameters = "k",
    ChiSqM_DF = "df",
    ChiSqM_PValue = "p",
    ChiSqBaseline_DF = "df",
    ChiSqBaseline_PValue = "p",
    ChiSqDiffTest_DF = "df",
    ChiSqDiffTest_PValue = "p",
    RMSEA_Estimate = "RMSEA"
  )  %>%
  flextable::set_table_properties(layout = "autofit")
```

\newpage

### Evidence of Correlational Validity

```{r correlation_matrix_lg, tab.cap = "Partial correlations among latent variables across time", tab.id = "correlation_matrix_lg", eval = params$correlation_matrix_lg}
# Factor correlation matrix from longitudinal models

df_cor_lg <- sup.cat(
  get.cor.lg(model = model_inv_lg[3], # the third one is always the scalar model
             path = model_file_path,
             string = ".WITH$"))

df_cor_lg <- df_cor_lg %>%
             tibble::rownames_to_column("variable") %>%
             dplyr::rename(" " = variable)

flextable::flextable(df_cor_lg) %>%
  flextable::add_footer_row(values = "Notes: Correlation estimates are obtained from the longitudinal invariance models.", colwidths =  ncol(df_cor_lg)) %>%
  flextable::add_footer_row(values = "* p < 0.05. ** p < 0.01. *** p < 0.001.", 
                  colwidths =  ncol(df_cor_lg)) %>%
  flextable::align(part = "all") %>% 
  flextable::font(fontname = "Times", part = "all") %>%
  flextable::bold(part = "header") %>%
  flextable::bold(j = " ", part = "body") %>%
  flextable::fontsize(size = 10, part = "all") %>% 
  flextable::italic(part = "footer") %>%
  flextable::set_table_properties(layout = "autofit")
```

\newpage

```{r correlation_matrix_bivar, tab.cap = "Bivariate correlations among factor scores", tab.id = "correlation_matrix_bivar", eval = params$correlation_matrix_bivar}
# Bivariate correlation matrix

df_cor_bivar <- get.cor.bivar(dat_fs)

df_cor_bivar <- df_cor_bivar %>%
            tibble::rownames_to_column("variable") %>%
            dplyr::rename(" " = variable)

flextable::flextable(df_cor_bivar) %>%
  flextable::add_footer_row(values = "Notes: Factor scores are obtained from the longitudinal invariance models", colwidths =  ncol(df_cor_bivar)) %>%
  flextable::add_footer_row(values = "* p < 0.05. ** p < 0.01. *** p < 0.001.", 
                  colwidths =  ncol(df_cor_bivar)) %>%
  flextable::align(part = "all") %>% 
  flextable::font(fontname = "Times", part = "all") %>%
  flextable::bold(part = "header") %>%
  flextable::bold(j = " ", part = "body") %>%
  flextable::fontsize(size = 10, part = "all") %>% 
  flextable::italic(part = "footer") %>%
  flextable::set_table_properties(layout = "autofit")
```

\newpage

```{r correlation_matrix_item, tab.cap = "Bivariate correlations among all items", tab.id = "correlation_matrix_item", eval = params$correlation_matrix_item}
# Bivariate correlation matrix among all items
# Warning!: this could be really long and takes some time to run, so the default is not to evaluate this chunk unless otherwise specified.

df_cor_item <- get.cor.bivar(dat_s)

df_cor_item <- df_cor_item %>%
            tibble::rownames_to_column("variable") %>%
            dplyr::rename(" " = variable)

flextable::flextable(df_cor_item) %>%
  flextable::add_footer_row(values = "* p < 0.05. ** p < 0.01. *** p < 0.001.",
                  colwidths =  ncol(df_cor_item)) %>%
  flextable::align(part = "all") %>%
  flextable::font(fontname = "Times", part = "all") %>%
  flextable::bold(part = "header") %>%
  flextable::bold(j = " ", part = "body") %>%
  flextable::fontsize(size = 10, part = "all") %>%
  flextable::italic(part = "footer") %>%
  flextable::set_table_properties(layout = "autofit")
```

\newpage

## Appendix

```{r cfa_model_thresholds, tab.cap = "CFA model thresholds at all waves", tab.id = "cfa_model_thresholds", eval = params$cfa_model_thresholds}
df_cfa_modthreshold <- sup.cat(
  lapply(model_cfa, 
         get.modthreshold, 
         path = model_file_path) %>% 
  purrr::reduce(dplyr::left_join, 
                by = c("paramHeader", "param")))

flextable::flextable(df_cfa_modthreshold) %>%
  flextable::align(part = "all") %>%
  flextable::font(fontname = "Times", part = "all") %>%
  flextable::bold(part = "header") %>%
  flextable::fontsize(size = 10, part = "body") %>% 
  flextable::set_table_properties(layout = "autofit")
```

\newpage

<!---BLOCK_LANDSCAPE_STOP--->

## Reference

Please use Zotero (or other reference managers) to add in-line citations and bibliography.

`r officer::block_section(ps)`
